---
title: Breath of the Wild Stream Highlights
author: Alexis Meskowski
date: '2020-11-11'
slug: [breath-of-the-wild-stream-highlights]
categories: [Game]
tags:
  - Nintendo Switch
  - Stream
  - Playthrough
  - breath of the wild
subtitle: ''
lastmod: '2020-11-11T22:14:55-06:00'
description: 'The compiled highlights of BotW from our Twitch streams!'
license: ''
resources:
- name: featured-image
  src: BotW-preview.png
- name: featured-image-preview
  src: BotW-preview.png
math:
  enable: false
share:
  enable: true
comment:
  enable: true
---

### Hello friends, here are the highlights of our Breath of the Wild playthrough! 

If you would like to visit the entire playlist directly on our YouTube channel you can click [here](https://www.youtube.com/watch?v=qhUAnu8ujIg&list=PL2lN_Ghz6kcJJhTB5kfDO-uHnNE9lRMmw){target="_blank"}. 

Or if you just want to see our YouTube channel, you can click [here](https://www.youtube.com/channel/UCDbvOR7EeHhe4_7CFtgW4Bg){target="_blank"}

This is our first playthrough of this game and we are *loving* it so far! We are having a lot of fun learning the game and interacting with our friends over on Twitch. If you would like to come hang out with us click [here](https://www.twitch.tv/koderkow/schedule){target="_blank"} to follow us, see when we will be streaming next, and get notified when we go live! 

### Stream Highlight #1

```{r, echo=FALSE}
blogdown::shortcode("youtube", "qhUAnu8ujIg")
```

### Stream Highlight #2

```{r, echo=FALSE}
blogdown::shortcode("youtube", "yFkVfy4lxpQ")
```

### Stream Highlight #3

```{r, echo=FALSE}
blogdown::shortcode("youtube", "v8ZDP0pPZZ8")
```

### Stream Highlight #4

```{r, echo=FALSE}
blogdown::shortcode("youtube", "1sk7su63VyI")
```